\newcommand{\symm}{\text{symm}}
\section{Introduction and Motivation}
\subsection{The Need for Hybrid Encryption}
For quite some time leading up to the present, symmetric and asymmetric key cryptosystems have been used extensively for securing communications in networks and among various parties; and both have their own merits and drawbacks. We will not go deep down into the details of these types of cryptosystems, but instead briefly discuss those to set the stage for the object of our attention - hybrid encryption.

In the case of symmetric key encryption, the sender (Alice) and receiver (Bob) share the same key (and therefore must share the key somehow to enable secure connection and decryption of the ciphertext by the receiver) that only they are privy to, and the sender uses said key to encrypt the message and sends the ciphertext to the receiver, who decrypts it with the aid of his knowledge of the secret key. Any third party/adversary would not be able to obtain any information about the message being sent by looking at the ciphertext, if this is implemented properly.\cite{smirnoff_turner_2019}

Asymmetric key encryption, also known as public key encryption or two-key encryption\cite{kaliski_acry}, requires the use of a pair of keys, one public key and the other one being a private key. The public key can be made visible to anyone without compromising the security of the communication and is used to encrypt messages, but the private key is to be kept secret at all times as it is used to decrypt any messages encrypted using the public key.\cite{savvyasym}

Symmetric key encryption is often faster and more efficient than asymmetric key encryption, and therefore it is preferable to use the former for encrypting large volumes of data, though it has severe drawbacks, viz. the reuse of the secret key in a symmetric cryptosystem leaks some information about the key and renders its use precarious with repetitive use and degrades the security of the communication, as the adversary can use the information she (Eve) gathers by looking at ciphertexts generated by using the same key repetitively to learn some information about the key in question.\cite{smirnoff_turner_2019}

On the other hand, asymmetric key encryption is more secure in this regard as knowledge of the public key does not enable the adversary to figure out the private key at all, even if those two keys are mathematically related in the construction of the cryptosystem. However, this amazing property of asymmetric key cryptosystems comes at a cost - they take are less efficient than symmetric key cryptosystems computationally, i.e. they are computationally intense, and this tradeoff means that asymmetric key cryptosystems are rendered impractical for the purpose of encrypting large volumes of data, as mentioned earlier. This definitely hampered the usability of asymmetric key cryptosystems and their adoption.

So the natural question is whether we can combine the efficiency of symmetric key encryption along with the strong security of asymmetric key encryption to produce a cryptosystem that gives us the best of both worlds? The answer is yes, and is found in the form of hybrid encryption.

\subsection{Basic Introduction to Hybrid Encryption}
So what we do with hybrid encryption is this - we use a symmetric key encryption scheme to encrypt the message itself, and then we use an asymmetric key encryption scheme to encrypt the key used in the symmetric key encryption part earlier. The former component of hybrid encryption with symmetric key encryption is called the \textit{data encapsulation mechanism}, or DEM for short, and the latter with asymmetric encryption is called the \textit{key encapsulation mechanism}, or KEM for short.\cite{kuro_he}

This is implemented in the following way, given that the sender is named Alice and the receiver is named Bob. (This has been described in great and more precise detail by Cramer and Shoup (2003)\cite{cryptoeprint:2001:108})
\begin{enumerate}
\item Alice obtains Bob's public key;
\item \textbf{DEM:} She then produces a fresh symmetric key $k_\text{symm}$ and then encrypts the message $m$ she wants to send using $k_\text{symm}$ to obtain a ciphertext $\chi$;
\item \textbf{KEM:} Note that only Alice possesses $k_\symm$ at this point in time, so she encrypts $k_\symm$ using Bob's public key (which is convenient, because symmetric keys in practice are usually and ideally of small and manageable sizes, and thus appropriate for public key encryption) to get $\psi$;
\item Alice sends $\bar\psi=(\psi,\chi)$ to Bob, and he decrypts it using his private key - first he verifies whether $\bar\psi$ properly encodes the tuple of ciphertexts $(\psi,\chi)$;
\begin{enumerate}
\item If not, then $\bar\psi$ is rejected and the process halts;
\item If yes, then $\psi$ is decrypted using Bob's private key; if this produces a reject, then the process is halted; if not, then he obtains the symmetric key $k_\symm$, using which he can decrypt $\chi$, the ciphertext pertaining to the message $m$, to get $m$ itself, if there's no issue that can possibly produce a reject.
\end{enumerate}
\end{enumerate}

What this essentially does is make the hybrid key encryption scheme essentially a public key (i.e. asymmetric key) encryption scheme and share in the security definitions of the same.
\label{sec:intro}
